### 2014-05-09 intro.tex
Clean up homog/heterog

We also measured the benefits and costs of adding ``TCP-awareness'' to
a computer-generated congestion-control protocol protocol. Including
the possibility of TCP cross-traffic in the network model improved
performance when TCP cross traffic was actually present---but hurt
performance when TCP cross traffic was absent, compared with a
``purebred'' protocol designed only to interoperate with itself.

>>>>

We also measured the benefits and costs of adding ``TCP-awareness'' to
a computer-generated congestion-control protocol protocol. Including
the possibility of TCP cross-traffic in the network model improved
performance when TCP cross traffic was actually present---but hurt
performance when TCP cross traffic was absent, compared with a
``TCP-naive'' protocol designed only to interoperate with itself.

### 2014-05-09 learn_operational.tex
Clean up homog/heterog

\begin{figure*}[b!]
%\centering
%\begin{subfigure}[b]{\columnwidth}
%\includegraphics[width=\columnwidth]{compatible-5sec.pdf}
%\caption{TCP-Aware and TCP-Naive RemyCCs, 5 second ON/OFF}
%\end{subfigure}
%
%\begin{subfigure}[b]{\columnwidth}
\caption{RemyCCs designed with and without TCP-awareness,
  competing against themselves or against TCP. Shown here, two
  endpoints contending for a 10~Mbps link with 100~ms RTT, 250 kB of
  buffer capacity (200~ms maximum queueing delay), and
  almost-continuous offered load. The fair share of throughput is
  5~Mbps per endpoint. Ellipses show 1-$\sigma$ range of results.}
%\end{subfigure}
\label{fig:tcpaware}
\begin{center}
\includegraphics[width=\textwidth]{figures/manual/compatibility-drawn.pdf}
\end{center}
\end{figure*}

@@

The results are shown in Figure~\ref{fig:tcpaware}. In the left panel,
protocols compete only with cross-traffic from the same protocol. In
this homogeneous setting, adding TCP-awareness to a RemyCC builds
up standing queues, more than doubling the queueing delay without
affecting throughput.

But in a mixed setting (Figure~\ref{fig:tcpaware}, right panel) where a RemyCC competes against TCP
NewReno, the TCP-naive RemyCC is squeezed out and does not get its fair
share of the link. In the shaded region showing the results when
NewReno competes with the TCP-aware RemyCC, TCP-awareness allows the RemyCC
to claim its fair share of the link and reduces the queueing delay
experienced both by itself and by TCP NewReno.

>>>>

\begin{comment}
\begin{figure*}[b!]
%\centering
%\begin{subfigure}[b]{\columnwidth}
%\includegraphics[width=\columnwidth]{compatible-5sec.pdf}
%\caption{TCP-Aware and TCP-Naive RemyCCs, 5 second ON/OFF}
%\end{subfigure}
%
%\begin{subfigure}[b]{\columnwidth}
\caption{RemyCCs designed with and without TCP-awareness,
  competing against themselves or against TCP. Shown here, two
  endpoints contending for a 10~Mbps link with 100~ms RTT, 250 kB of
  buffer capacity (200~ms maximum queueing delay), and
  almost-continuous offered load. The fair share of throughput is
  5~Mbps per endpoint. Ellipses show 1-$\sigma$ range of results.}
%\end{subfigure}
\label{fig:tcpaware}
\begin{center}
\includegraphics[width=\textwidth]{figures/manual/compatibility-drawn.pdf}
\end{center}
\end{figure*}
\end{comment}

@@

\begin{figure}
\caption{Performance of two flows of the same congestion-control
  scheme contending for a 10~Mbps link, for three different
  congestion-control schemes. The ``TCP-naive'' RemyCC is designed
  under the assumption that its competition, when present, is governed
  by the same RemyCC---an assumption that holds here. The
  ``TCP-aware'' RemyCC is designed under the assumption that its cross
  traffic has a 50\% chance of being governed by a TCP AIMD-like
  scheme. The results quantify the degree to which designing a
  protocol to play well with TCP can exact a cost when TCP is absent.}
\label{fig:tcphomog}
\begin{center}
\includegraphics[width=\textwidth]{homo-3.pdf}
\end{center}
\end{figure}

\begin{figure}
\caption{When cross traffic is governed by TCP NewReno, the TCP-aware
  RemyCC achieves a more equitable division of the link---and better
  delay for both flows---than the TCP-naive RemyCC. The results
  demonstrate the benefit of TCP-awareness when TCP is present.}
\label{fig:tcpheterog}
\begin{center}
\includegraphics[width=\textwidth]{hetero-3.pdf}
\end{center}
\end{figure}

In Figure~\ref{fig:tcphomog}, protocols compete only with
cross-traffic from the same protocol. In this homogeneous setting,
adding TCP-awareness to a RemyCC builds up standing queues, more than
doubling the queueing delay without affecting throughput.

But in a mixed setting (Figure~\ref{fig:tcpheterog}) where a RemyCC
competes against TCP NewReno, the TCP-naive RemyCC is squeezed out and
does not get its fair share of the link. In the shaded region showing
the results when NewReno competes with the TCP-aware RemyCC,
TCP-awareness allows the RemyCC to claim its fair share of the link
and reduces the queueing delay experienced both by itself and by TCP
NewReno.
